The Effect of a Second AIDS Defining Illness on Survival in the MACS

### 2015-04-21 R/paper.Rmd
Paste link

```{r chunks, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

@@

visits %>%
    group_by(id) %>%
    summarise(sec.aids=min(sec.aids.diag)) %>%
    mutate(sec.aids=plyr::revalue(as.character(sec.aids),
                                  c("0"="No Aids",
                                    "1"="PCP",
                                    "2"="KS",
                                    "3"="NHL",
                                    "4"="Neuro",
                                    "5"="Bacteria OI",
                                    "6"="Fungal OI",
                                    "7"="Protozoa",
                                    "8"="CMV/HSV",
                                    "9"="Wasting",
                                    "10"="Recurrent PNA",
                                    "11"="Cervical Ca"))) %>%
ggplot(., aes(x=sec.aids)) + geom_histogram() +
    xlab("Type of Secondary Aids Diagnosis") +
    ylab("Count") +
    ggtitle("Figure 1") +
    theme(axis.text.x = element_text(angle=-45))
```

>>>>

```{r chunks, echo=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      message=FALSE)
```

@@

visits %>%
    group_by(id) %>%
    summarise(sec.aids=min(sec.aids.diag)) %>%
    mutate(sec.aids=plyr::revalue(as.character(sec.aids),
                                  c("0"="No Aids",
                                    "1"="PCP",
                                    "2"="KS",
                                    "3"="NHL",
                                    "4"="Neuro",
                                    "5"="Bacteria OI",
                                    "6"="Fungal OI",
                                    "7"="Protozoa",
                                    "8"="CMV/HSV",
                                    "9"="Wasting",
                                    "10"="Recurrent PNA",
                                    "11"="Cervical Ca")),
           warn_missing=FALSE) %>%
ggplot(., aes(x=sec.aids)) + geom_histogram() +
    xlab("Type of Secondary Aids Diagnosis") +
    ylab("Count") +
    ggtitle("Figure 1") +
    theme(axis.text.x = element_text(angle=-90)) +
    scale_x_discrete(limits=k
```

```{r naive-survival}
# http://cran.r-project.org/web/packages/survival/vignettes/timedep.pdf
```
